# Results

a) Which part of NYC has restaurants with relatively low grades and relatively high grades?
 
b) Is there a relationship between the type of restaurants and the type of violations?

c) For the franchise restaurants, what type of violations are most common and what might be the reasons?

```{r}
library(tidyverse)
library(dplyr)
```

1. First, take a look at the distributions of all restaurants inspected in NYC. Each point in the following map represents a unique restaurant. It is clear that Manhattan has the highest density of restaurant distribution among all boroughs. The density is also quite high along the coastline for Queens and Brooklyn compared to the densities in the other areas.

```{r}
library(ggmap)
register_google(key="AIzaSyBrIvXrqMDIGTB8kH6g5YSTSlOxVcknHas")
has_google_key()
```

```{r}
nyc_map <- get_map(location = c(lon = -74.00, lat = 40.71), maptype = "terrain", zoom = 11)

ggmap(nyc_map)+ 
  geom_point(aes(x=restaurant$Longitude,y=restaurant$Latitude),data=restaurant,alpha=0.1,size=0.7)
```

Here is an interactive map to show the number of restaurants in each selected area. Zoom-in and Zoom-out allow for inspection on smaller and larger scale.

```{r}
library(leaflet)
library(leaflet.extras)
library(htmltools)
restaurant %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    radius = 2,
    label = ~ htmlEscape(`DBA`),
    clusterOptions = markerClusterOptions()
  ) 
```

```{r}
lat <- mean(restaurant$Latitude)
lon <- mean(restaurant$Longitude)

leaflet(restaurant) %>%
  addProviderTiles(providers$CartoDB.DarkMatterNoLabels) %>%
  addWebGLHeatmap(size = 15, units = "px")  %>%
  setView(lng = lon, lat = lat, zoom = 10)
```



2. Now we will take a look at the cuisine type of all restaurants inspected. we notice that American and Chinese cuisines take a large percentage in the restaurants inspected. Since the dataset is quite general on all active restaurants in NYC, we can tell that most of the restaurants are American or Chinese in NYC. The number of American restaurants is over 80,000, which is quite surprising for us as this number is much larger than we thought it to be.

```{r}
library(treemap)
type_number<-restaurant %>%
  group_by(CUISINE.DESCRIPTION) %>%
  summarise(n=n())
```

```{r}
treemap(type_number,
        index=c("CUISINE.DESCRIPTION"),
        vSize="n",
        vColor="n",
        type="value")+
  ggt
```


3. Now we are interested in exploring whether there is a relationship between boroughs and cuisine types. Here we use a stacked bar chart with each bar representing a certain cuisine type and fill each bar according to the percentage of this type in each borough. Note that we only take into account the cuisine types with quantities over 200 in each borough to reduce the complexity of the chart and make it more clear.

```{r}
type_boro<-restaurant %>%
  group_by(CUISINE.DESCRIPTION,BORO) %>%
  summarize(count=n()) %>%
  filter(count>200)%>%
  mutate(prop=count/sum(count)) %>%
  ungroup()

ggplot(type_boro,aes(x=CUISINE.DESCRIPTION,fill=BORO,y=prop)) +
  geom_bar(stat="identity") #+ 
  #coord_flip()
```




4. Now we take a look at the grades according to each cuisine type. 

```{r}
type_grade<-restaurant %>%
  group_by(CUISINE.DESCRIPTION,GRADE) %>%
    summarize(count=n()) %>%
  mutate(prop=count/sum(count)) %>%
    filter(GRADE %in% c("A","B","C","G","N","P","Z"))%>%
  ungroup()
# 如何按照A 的比例排序？
ggplot(type_grade,aes(x=fct_reorder2(CUISINE.DESCRIPTION,GRADE=="A",GRADE,.desc=FALSE),fill=GRADE,y=prop)) +
  geom_bar(stat="identity", position="fill") #+ 
  #coord_flip()
```

```{r}
library(GGally)
library(ggpubr)

type_grade<-restaurant %>%
  group_by(CUISINE.DESCRIPTION,GRADE) %>%
    summarize(count=n()) %>%
  mutate(prop=count/sum(count)) %>%
    filter( GRADE %in% c("A","B","C","G","N","P","Z"))%>%
  ungroup()
#type_grade
type_grade$CUISINE.DESCRIPTION<-as.character(type_grade$CUISINE.DESCRIPTION)
#factor(type_grade$CUISINE.DESCRIPTION)

type_grade_mess<-type_grade%>%
    filter(count>500) %>%
  select(-c(count)) 

type_grade_mess<-pivot_wider(data=type_grade_mess,id_cols=CUISINE.DESCRIPTION,names_from=GRADE,values_from=prop)


ggballoonplot(type_grade, x = "CUISINE.DESCRIPTION", y = "GRADE", size = "prop",
              fill = "count", 
              ggtheme = theme_bw()) +
  scale_fill_viridis_c(option = "C")
```

```{r}
ggpairs(data=type_grade_mess,columns=1:2,cardinality_threshold =90)
```


5. Then we consider that the boroughs might also have some effects on the grades of restaurants, so we explore the grades of restaurants in different boroughs.
```{r}
restaurant<-restaurant[(!restaurant$BORO=="0")& restaurant$GRADE 
                       %in% c("A","B","C","G","N","P","Z") & (!restaurant$Latitude =="0") & (!restaurant$GRADE =='NA') & (!restaurant$BORO =='NA'),] %>%
  mutate(BORO_abb=substr(BORO,0,4))

ggplot(restaurant)+
  geom_bar(aes(x=BORO_abb))+
  facet_wrap(~GRADE,scale="free")+
  theme(axis.text.x = element_text(angle=45, hjust=1))
```
From the bar charts above, we can get the general idea of how the grades are related to boroughs. Since the distributions of the number of restaurants in each borough are very similar under each score, we can conclude that the grades of restaurants have almost no relationship with boroughs.

To get a more detailed view of the relationship, we draw another version of the same data below. Here we count the proportion of each grade in each borough. Note that this bar chart makes more sense since it is the proportion that really matters instead of the number itself.

```{r}
type_grade<-restaurant %>%
  group_by(BORO,GRADE) %>%
  filter(!BORO=='0') %>%
    summarize(count=n()) %>%
  mutate(prop=count/sum(count)) %>%
    filter(GRADE %in% c("A","B","C","G","N","P","Z"))%>%
  ungroup()
# 如何按照A 的比例排序？
ggplot(type_grade,aes(x=BORO,fill=GRADE,y=prop)) +
  geom_bar(stat="identity") + 
  coord_flip()
```

The graph above shows the same result as we mentioned before-the grades of restaurants are not much affected by the boroughs. We can tell that although the proportion of each grade differs a little for each borough, there is no big difference that worth taking into account.



6. Will restaurants have different types of violations according to thier cuisine types? Here we try to find out whether there is a relationship between the cuisine types and the violation types accordingly. Since there are a total of 84 cuisine types and a total of 75 violation types, which will be too complicated if all been used, we only choose the 14 most common cusine types and the 10 most common violation types in this case.

```{r}
type_sample <- restaurant %>%
  group_by(CUISINE.DESCRIPTION) %>%
  summarise(num=n()) %>%
  filter(num>3000)

violation_sample <- restaurant %>%
  group_by(VIOLATION.CODE) %>%
  summarise(num=n()) %>%
  filter(num>4000)
```

```{r}
type_violation <- rest_sample %>%
  mutate(cus_abb=substr(CUISINE.DESCRIPTION,0,4)) %>%
  filter(CUISINE.DESCRIPTION %in%  
           as.vector(type_sample$CUISINE.DESCRIPTION)) %>%
  filter(VIOLATION.CODE %in% 
           violation_sample$VIOLATION.CODE) %>%
  group_by(cus_abb, VIOLATION.CODE) %>%
  filter(!cus_abb=='NA') %>% 
  summarize(count=n()) %>%
  mutate(prop=count/sum(count)) %>%
  ungroup()
```

```{r}
ggplot(type_violation,aes(x=cus_abb,y=prop,
                          fill=VIOLATION.CODE)) +
  geom_bar(stat="identity")+
  theme(axis.text.x = element_text(angle=45,hjust=1))
```

Above is the graph showing the proportion of violation types for each cuisine type. it's not hard to identify that the bars for violation code 10F are higher much higher for restaurants of cuusine types "Cafe" and "Dounts". The restaurants of cuisine type "chicken" also have relatively high proportion of violation type 10F. 
***explanation needed***



7. There are a number of franchise restaurants in NYC, including Starbucks, Subway, Burgur King and so on. We want to identify the most common violation types for each franchise. We choose the franchise with more than 500 restaurants, which are the 9 franchises with the largest numbers of restaurants. Since there are a number of violation types, we choose 13 most common violation types among all. 

The franchises selected are "BURGER KING", "CROWN FRIED CHICKEN", "DUNKIN'", "DUNKIN', BASKIN ROBBINS", "KENNEDY FRIED CHICKEN", "MCDONALD'S", "POPEYES", "STARBUCKS" and "SUBWAY".

```{r}
franchise_name <- restaurant %>%
  group_by(DBA) %>%
  summarise(num=n()) %>%
  filter(num>500)

franchise_name
```

Here we select the most common violation types.
```{r}
violation_code <- restaurant %>%
  group_by(VIOLATION.CODE) %>%
  summarise(num=n()) %>%
  filter(num>3000)

violation_desc <- violation %>%
  filter(VIOLATION.CODE %in%  
           as.vector(violation_code$VIOLATION.CODE))
violation_desc
```

```{r}
franchise <- restaurant %>%
  filter(DBA %in% as.vector(franchise_name$DBA) &
       VIOLATION.CODE %in% 
         as.vector(violation_code$VIOLATION.CODE)) %>%
  mutate(DBA_abb=substr(DBA,0,3)) %>%
  group_by(DBA, VIOLATION.CODE) %>%
  summarise(num=n()) %>%
  mutate(prop=num/sum(num))
```

```{r}
ggplot(franchise_order) +
  geom_col(aes(x=VIOLATION.CODE,y=prop)) +
  facet_wrap(~DBA) + 
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

Above is the graph showing the proportion of violation types for each franchise. Note that the violation type with violation code 10F is the most common one for all of the franchises. The description of this violation is "Non-food contact surface improperly constructed. Unacceptable material used. Non-food contact surface or equipment improperly maintained and/or not properly sealed, raised, spaced or movable to allow accessibility for cleaning on all sides, above and underneath the unit." 

The violation types with codes 10B and 08A are also very common among all restaurants, with the descriptions-"Plumbing not properly installed or maintained; anti-siphonage or backflow prevention device not provided where required; equipment or floor not properly drained; sewage disposal system in disrepair or not functioning properly." and "Facility not vermin proof. Harborage or conditions conducive to attracting vermin to the premises and/or allowing vermin to exist."
***explanation needed***